Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-04-30 Manuscript.Rmd
done with Joe's revisions, including forcing APA reference style

---
title: 'Individual heterogeneity in the functional network topography of the medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
  word_document: 
    reference_docx: APA_style.docx #Style_reference_draft.docx 
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
---

@@

We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity. First, we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by examining three sets of spatial correlations across vertices between days: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps. These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]). We therefore compared the within-subject correlation coefficients produced by each method through a paired permutation analysis. For each of the 100 individuals, we computed the difference in inter-day correlations between methods, randomly alternated the sign of these values 5000 times, and computed the mean of these differences on each iteration. The empirical difference in means was then evaluated against this permuted distribution.

@@

Next, we examined the similarity of partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`). Qualitative inspection of the community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects. To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3). The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, V = `r mPFCvs0_wilcox$statistic`, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).

@@

We next explored the possible advantage of community detection relative to a simple seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC. We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations. We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC. We compared the map of correlation values in mPFC to the map of unbinarized Fiedler vector values. We performed pairwise spatial Spearman correlations among maps computed for each day and method from all subjects. For `r nrow(unCorrParticipants %>% filter(Corrs < 0))` subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted). ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar. We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days. Figure 7 (left) shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.

Figure 7 (right) shows the test/re-test reliability across days for patterns dervied using community detection, seed-based correlation, and across methods (e.g. Day 1 community detection versus Day 2 seed-based correlation). While both approaches were reliable, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`). Agreement across methods was fair, signifying that the two approaches identified similar topographic features but also systematic differences. These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies.

### *Similarities with other work*

The thresholded partitions in our work qualitatively resembled the topographical arrangement of DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017]. We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects. In their original work, Braga and Buckner manually selected individual vertices along areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two anticorrelated networks [@Braga2017; @Braga2019]. Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our prtitionings by selecting seeds in one these diagnostic areas. We confirmed seed placement based on the pattern observed in TPJ and PHC. The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 8.

Visual inspection of these networks shows a remarkable similarity between our DN and non-DN communities and the previously reported sub-networks A and B. Since our search space did not contain areas TPJ and PHC, lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs (particularly for network A). Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of two distinct communities. Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying the two communities in individuals.

@@

- Summarize the results
- Ours are not the first to show variability across individuals, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences. They also use parcellations for networks, whereas we focused on individual vertices to gain spatial finesse. Also, to the best of our knowledge we are the first to quantify the organizational heterogeneity of these areas in the human brain. 
- We are also not the first to show functional subdivision of DN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga). Our results are complementary in the sense that we show similar outcomes in 100 subjects. The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
- Stability within subject has also been shown before. This work was done using either parcellations and oversampling though. [@Laumann2015; @Gordon2017; @Braga2017; @Gratton2018b; @Kong2018]
- Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.
- Similarity with B&B: One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks. Based on our criteria, network B would more closely identify with DN (per 7m affiliation), while we currently do not have enough evidence to label network A. These discrepancies should be addressed with explicit behavioral manipulations in the future. Also our search space is limited compared to theirs, thus making the patterns only partially similar.
- The main gap is mapping behavior to functional organization, but we will do that with behavioral manipulations of subjective value in the future. Instead, we focus on understanding the importance of individualized mapping in these areas first, as a baseline.
- Clinical implications: individualized targets, and more accurate estimation of impacts based on assessment of individual patients. Similarly, our approach focuses on individual estimations without group priors, so it's well fit to address the problem of low n in clinical research. Also, SP can produce these effects with moderate amounts of data. Previous results suggest impractical amounts.

- Limitations
  - community detection ground truth
  - other algorithms (benefit of SP is that it's deterministic, allows for diagnostics, and discourages extremely large/small communities)
  - bipartition: we focus on that since we tried to capture what belongs to DN and non-DN. This intuition can be generalized to other behaviors. SP can be expanded to extract additional communities in combination with k-means and the identification of the first non-zero eigenvalue in the low-high rank.
  - Small search space: working at the vertex-level makes it computationally difficult to produce estimates at the whole-brain level.

- Joe:
  - something to potentially discuss later in the paper: for this to be maximally useful in the future, it would help if a general threshold can be identified (without having to do the windowed analysis on every subject). Looking at the amount variability in the per-subject thresholds might give us a sense of whether that's possible.

<!--

@@

We would like to thank Dan Sussman for initial guidance on community detection and evaluation methods. This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304). Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature. B: common and unique brain regions associated with DN and subjective value. DN regions defined by Yeo et al. (2011) in blue, which encompass areas of considerable overlap between DN and SV. Literature-specific regions (bilateral 7m and right v23 in yellow, and bilateral 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
# Change to inflated eventually
include_graphics("./Images/ROIS4.png")
```

@@

```{r Template partition (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
# if you want to rescale the range of values, use scales::rescale(vecot, c(min, max))
include_graphics("./Images/FB_FV_example.png")
```

@@

``` {r Partition comparison: all 2 (Fig. 3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
# code to produce the plot
# par(xpd = T)
# corrplot(abs(RI_PCC), # absolute for display purposes only, as it avoids the couple of negative ARIs and evens out the color bar
#          is.corr = F, 
#          method = "color",
#          type = "lower", 
#          tl.pos = "n", 
#          tl.cex = 0.1, 
#          cl.lim = c(0,1),
#          cl.length = 3,
#          #addgrid.col = "grey99",
#          cl.pos = "r",
#          mar = c(1,1,2,0))
# corrplot(RI_PFC, 
#          is.corr = F, 
#          method = "color", 
#          type = "upper", 
#          tl.pos = "n", 
#          tl.cex = 0.1,
#          cl.pos = "n",
#          #addgrid.col = "grey90",
#          mar = c(1,1,2,0), 
#          add = T)
# segments(0.5,0.5,0.5,100.5, lwd = 2)
# segments(0.5,0.5,100.5,0.5, lwd = 2)
# segments(0.5,100.5,100.5,100.5, lwd = 2)
# segments(100.5,0.5,100.5,100.5, lwd = 2)
# mtext(expression(bold("Subject Partitions")), line = 3)
# mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
# mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
# mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37). B: Proportion of times each vertex was affiliated with the DN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram counts the mean number of vertices that were affiliated at each proportion.", echo=FALSE, message = FALSE}
# code to generate plots

@@

```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom). Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices). B: Spatial mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample. This aggregate map shows the common organizational principle of the DN and non-DN communities, while also pinpointing the relatively high level of variability in mPFC."}

@@

``` {r Partition comparison: halves and runs (Fig. 6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 days of scans each), showing pattern agreement across days and subjects for PCC and mPFC separately. Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in the latter. Right: within-to-between subject mean ARI ratios for each subject again show higher idiosyncratic organization for mPFC.", echo=FALSE, message = FALSE}
### code for plots in this fig

@@

``` {r Correlation vs community detection (Fig. 7), fig.align="center", fig.cap = "A: Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector. There is high agreement within method (diagonal quadrants), but both methods suggest similar partitions (off-diagonal quadrants). B: Day 1 vs Day 2 correlation coefficients for every method, as well as between methods. Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo = FALSE, message = FALSE}
# code to produce the plots

>>>>

---
title: 'Individual heterogeneity in the functional network topography of the medial prefrontal cortex'
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
output:
  pdf_document: 
    keep_tex: true
    highlight: haddock
  word_document: 
    reference_docx: APA_style.docx #Style_reference_draft.docx 
  html_document: default
bibliography: mPFC_paper.bib
csl: apa.csl
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage[left]{lineno}
    - \linenumbers
---

@@

We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity. First, we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately. We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP across days in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps. Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices. These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. For 3 subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted). ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar. We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.

The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]). We therefore compared the within-subject correlation coefficients produced by each method through a paired permutation analysis. For each of the 100 individuals, we computed the difference in inter-day correlations between methods, randomly alternated the sign of these values 5000 times, and computed the mean of these differences on each iteration. The empirical difference in means was then evaluated against this permuted distribution.

@@

Next, we examined the similarity of partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`). Qualitative inspection of the community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects. To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3). The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).

@@

We next explored the possible advantage of community detection relative to a typical seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC. We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations. We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC. We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations. Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals. Figure 7 (left) shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.

Figure 7 (right) shows the test/re-test reliability across days for patterns dervied using community detection, seed-based correlation, and across methods (e.g. Day 1 community detection versus Day 2 seed-based correlation). While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`). Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences. These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies.

### *mPFC community structure resembles a proposed DN sub-network organization*

The thresholded partitions in our work qualitatively resembled the topographical arrangement of DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017]. We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects. In their original work, Braga and Buckner manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019]. Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our partitionings by selecting seeds in these diagnostic areas. We confirmed seed placement based on functional connectivity patterns observed in TPJ and PHC. The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed with the corresponding community detection results in Figure 8.

Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. A potential explanation is that SP fractionated the search space into communities that are maximally distant in function, whereas the sub-networks proposed by Braga and Buckner are still considered to be part of DN. Subthreshold vertices in the SP partitionings partially overlap with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A (the DN community) and other networks.

Understanding the interaction of these three networks requires future study. Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of at least two distinct communities. Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying these communities in individuals.

@@

  - It matters whether distinct cognitive functions overlap in the brain. Apparent overlap has motivated theoretical proposals about ways in which seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes.

  - The interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. Individual-level effects wash out in group averages (Michalka), apparent overlap in functional activation can vanish with increases in spatial precision (Woo), and resting-state networks have reliable individual-specific characteristics (Muller, Braga).

  - We don't yet really understand how much individual-level heterogeneity there is in the functional topography of mPFC. We need to (1) develop an efficient/robust method to capture individual-level topography, and (2) quantify the degree of heterogeneity in a large group of individuals.

  - The method we propose is spectral partitioning. Restricting our analyses to a general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis. SP has advantages (deterministic, simple diagnostics). Comparisons with modularity maximization suggested the binary partitioning was appropriate.

  - The community structure identified by SP was reliable across test/re-test and was heterogeneous across individuals. The heterogeneity was especially large in mPFC.

  - There are various potential sources of the heterogeneity. Could be gross anatomy (varying sulcal patterns; Mackey). Could also be shifts in function relative to anatomy (Haxby hyperalignment). Could be connectivity (Passingham, Mars, Tobyne). A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture (Glasser), or structural connectivity/white matter microstructure (Saygin & Kanwisher).

   - SP is data-driven and the communities don't come with labels. We applied labels based on the meta-analysis. We were able to apply group-level labels on the basis of the topography in PCC, where functional organization was more consistent across individuals. Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.

  - Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio (fewer individuals and more data per individual; Gordon, Braga, Poldrack). We've been able to quantify the variability in a large sample, and our method does not require massively multi-session data acquisition.

  - We found SP results could be made more stable by thresholding the underlying Fiedler vector. We used temporal stability to apply a custom threshold per subject, but there might be ways to use a generalized threshold in the future.

  - SP outperformed seed-based correlation. This makes sense, since it makes use of more information (n(n-1)/2 pairwise correlations, rather than n correlations with the seed).

  - Our work is complementary with Braga & Buckner. They identified subdivisions, whereas we've identified variable topography for the DN as a whole.

  - Limitations. Our approach is (by design) more anatomically focal. A binary partitioning is undoubtedly only an approximation of the ground truth. Etc.

  - Future directions. This could be used to identify individualized units of analysis (ROIs) for task activation studies. This might be useful in clinical studies, or in studies aiming to dissociate different forms of valuation, or to reach a stronger conclusion as to whether valuation and DMN processes are topographically segregable or colocalized.

<!--
- Summarize the results
- Ours are not the first to show variability across individuals, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences. They also use parcellations for networks, whereas we focused on individual vertices to gain spatial finesse. Also, to the best of our knowledge we are the first to quantify the organizational heterogeneity of these areas in the human brain. 
- We are also not the first to show functional subdivision of DN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga). Our results are complementary in the sense that we show similar outcomes in 100 subjects. The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
- Stability within subject has also been shown before. This work was done using either parcellations and oversampling though. [@Laumann2015; @Gordon2017; @Braga2017; @Gratton2018b; @Kong2018]
- Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.
- Similarity with B&B: One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks. Based on our criteria, network B would more closely identify with DN (per 7m affiliation), while we currently do not have enough evidence to label network A. These discrepancies should be addressed with explicit behavioral manipulations in the future. Also our search space is limited compared to theirs, thus making the patterns only partially similar.
- The main gap is mapping behavior to functional organization, but we will do that with behavioral manipulations of subjective value in the future. Instead, we focus on understanding the importance of individualized mapping in these areas first, as a baseline.
- Clinical implications: individualized targets, and more accurate estimation of impacts based on assessment of individual patients. Similarly, our approach focuses on individual estimations without group priors, so it's well fit to address the problem of low n in clinical research. Also, SP can produce these effects with moderate amounts of data. Previous results suggest impractical amounts.

@@

We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Dan Sussman for initial guidance on community detection and evaluation methods. This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304). Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details)."}
# Change to inflated eventually
include_graphics("./Images/ROIS4.png")
```

@@

```{r Representative partitioning (Fig. 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
# if you want to rescale the range of values, use scales::rescale(vecot, c(min, max))
include_graphics("./Images/FB_FV_example.png")
```

@@

``` {r Partitioning comparison: all (Fig. 3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. Functional topographic patterns were better aligned across individuals in PCC than mPFC.", echo=FALSE, message = FALSE}
# code to produce the plot
# par(xpd = T)
# corrplot(abs(RI_PCC), # absolute for display purposes only, as it avoids the couple of negative ARIs and evens out the color bar
#          is.corr = F, 
#          method = "color",
#          type = "lower", 
#          tl.pos = "n", 
#          tl.cex = 0.1, 
#          cl.lim = c(0,1),
#          cl.length = 3,
#          #addgrid.col = "grey99",
#          cl.pos = "r",
#          mar = c(1,1,2,0))
# corrplot(RI_PFC, 
#          is.corr = F, 
#          method = "color", 
#          type = "upper", 
#          tl.pos = "n", 
#          tl.cex = 0.1,
#          cl.pos = "n",
#          #addgrid.col = "grey90",
#          mar = c(1,1,2,0), 
#          add = T)
# segments(0.5,0.5,0.5,100.5, lwd = 2)
# segments(0.5,0.5,100.5,0.5, lwd = 2)
# segments(0.5,100.5,100.5,100.5, lwd = 2)
# segments(100.5,0.5,100.5,100.5, lwd = 2)
# mtext(expression(bold("Subject Partitions")), line = 3)
# mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
# mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
# mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (1 min shift, i.e. ~84 TRs). B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (bottom). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram displays the frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
# code to generate plots

@@

```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom). Subthreshold values effectively formed a third community of high-variability vertices. B: mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample. This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the relatively high level of variability in mPFC."}

@@

``` {r Partition comparison: halves and runs (Fig. 6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately. Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in mPFC. Right: within-to-between subject mean ARI ratios for run-specific partitionings again show higher subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
### code for plots in this fig

@@

``` {r Correlation vs community detection (Fig. 7), fig.align="center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector. The upper-right and lower-left quadrants show across-method agreement. B: Day 1 vs Day 2 correlation coefficients for each method, as well as between methods. Community detection through spectral partitioning provided more stable estimates, even though both methods showed good level of agreement.", echo = FALSE, message = FALSE}
# code to produce the plots
